---
title: "`r params$company_long`"
output:
    bookdown::pdf_document2:
        latex_engine: xelatex
        keep_tex: false
        template: template.tex
        number_sections: true
params:
    company_short: ""
    company_long: ""
    cals_start_1: "2021-08-03"
    cals_start_2: "2022-03-01"
    all_comparison_1_start: "2021-09-01"
    all_comparison_2_start: "2022-03-01"
    species: !r c("NO2", "O3", "PM2.5")
    average: "hour"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=F, warning=F, dev="pdf", fig.pos="!H")
options(dplyr.summarise.inform = FALSE)
library(tidyverse)
library(lubridate)
library(odbc)
library(ggpubr)
library(cowplot)
library(ggtext)
library(knitr)
library(odbc)
library(kableExtra)
library(ggpointdensity)
library(RColorBrewer)
library(latex2exp)
library(quantr)
```

```{r}
# Uncertainty and LV are provided in ugm3 and need converting to ppb
REU_PROPERTIES <- list(
    "O3" = list(
        "uncertainty_ugm3"=1.10,
        "LV_ugm3"=120,
        "DQO_pct"=30
    ),
    "NO2" = list(
        "uncertainty_ugm3"=0.49,
        "LV_ugm3"=200,
        "DQO_pct"=25
    ),
    "PM2.5" = list(
        "uncertainty"=0.48,
        "LV"=30,
        "DQO_pct"=50
    )
)
# Using the EC conversion factors at 20C
# https://uk-air.defra.gov.uk/assets/documents/reports/cat06/0502160851_Conversion_Factors_Between_ppb_and.pdf
ppb_to_ugm3 <- list(
    "O3" = 1.9957,
    "NO2" = 1.9125
)
for (gas in c("O3", "NO2")) {
    REU_PROPERTIES[[gas]][["uncertainty"]] <- REU_PROPERTIES[[gas]][["uncertainty_ugm3"]] / ppb_to_ugm3[[gas]]
    REU_PROPERTIES[[gas]][["LV"]] <- REU_PROPERTIES[[gas]][["LV_ugm3"]] / ppb_to_ugm3[[gas]]
}
```

```{r}
CALS_1_START <- as_datetime(params$cals_start_1)  # can't directly pass params$cals_start into SQL queries
CALS_2_START <- as_datetime(params$cals_start_2)  # can't directly pass params$cals_start into SQL queries
ALL_COMPARISON_1_START <- as_datetime(params$all_comparison_1_start)  # can't directly pass params$cals_start into SQL queries
ALL_COMPARISON_2_START <- as_datetime(params$all_comparison_2_start)  # can't directly pass params$cals_start into SQL queries
STUDY_1_END <- as_datetime("2022-01-25 23:59:59")
STUDY_2_END <- as_datetime("2022-06-14 23:59:59")
EARLIEST_TIME_1 <- min(CALS_1_START, ALL_COMPARISON_1_START)
EARLIEST_TIME_2 <- min(CALS_2_START, ALL_COMPARISON_2_START)
```

```{r}
# Get handle to the QUANT db where data is stored
con <- dbConnect(odbc(), "QUANT")
```

```{r}
# Find all devices that have data for
all_devices <- tbl(con, "lcsinstrument") %>% 
    filter(study == 'Wider Participation',
           instrument != 'IMB1') |>  # Device failed in March 2022
    collect() %>%
    filter(company == params$company_short) |>
    arrange(instrument) %>%
    pull(instrument)

# Create lookup-table with the company's internal device ID
device_lut <- tbl(con, "lcsinstrument") |>
    filter(study == 'Wider Participation') |>
    select(id=instrument, webid=internalid) |>
    collect()
```

```{r}
retrieve_lcs_data <- function(devices, start, end, species, avg=NULL) {
    df <- tbl(con, "measurement") %>%
        filter(instrument %in% devices,
               time >= start, time <= end,
               sensornumber == 1,
               measurand %in% species) %>%
        left_join(tbl(con, "flag"), 
                  by=c("time", "instrument", "measurand", "sensornumber", "calibrationname")) |>
        filter(is.na(flagtype) | flagtype != 'Error') |>
        select(timestamp=time, instrument, measurand, measurement)
    
    if (!is.null(avg)) {
        df <- df %>%
            mutate(timestamp = floor_date(timestamp, avg)) %>%
            group_by(timestamp, instrument, measurand) %>%
            summarise(measurement = mean(measurement, na.rm=T)) |>
            ungroup()
    }
    df |>
        collect()
}
```

```{r}
# Download LCS data and switch to using the company's internal ID
lcs <- retrieve_lcs_data(all_devices,
                         CALS_2_START,
                         STUDY_2_END,
                         params$species,
                         avg=params$average) %>%
        inner_join(device_lut, by=c("instrument"="id")) %>%
        select(-instrument, device=webid)
```

```{r}
# Add reference data
species_to_pull <- params$species
avg <- params$average
ref <- tbl(con, "ref") %>%
        filter(location == "Manchester",
               measurand %in% c(species_to_pull, 'Temperature', 'RelHumidity'),
               time >= EARLIEST_TIME_2, time <= STUDY_2_END) %>%
        select(timestamp=time, measurand, measurement) %>%
        mutate(timestamp = floor_date(timestamp, avg)) %>%
        group_by(timestamp, measurand) %>%
        summarise(measurement = mean(measurement, na.rm=T)) %>%
        ungroup() %>%
        collect()
```

```{r}
# Combine LCS and Ref
comb <- lcs %>%
            full_join(ref, by=c("timestamp", "measurand"), suffix=c("_lcs", "_ref"))

# Add all possible hours
all_hours <- seq.POSIXt(from=CALS_2_START, to=STUDY_2_END, by="1 hour")
all_hours_df <- expand.grid(timestamp=all_hours,
                         device=device_lut %>% filter(id %in% all_devices) %>% distinct(webid) %>% pull(webid),
                         measurand=params$species) %>%
                as_tibble()
comb <- all_hours_df %>%
            left_join(comb, by=c("timestamp", "device", "measurand")) |>
            rename(species = measurand, lcs = measurement_lcs, ref = measurement_ref)
```

# QUANT Wider Participation Study

This is the second Wider Participation Study (WPS) assessment report on the sensor systems provided by `r params$company_long` that were monitored as part of the Wider Participation extension of the [QUANT study](https://www.ukcleanair.org/projects/quant-quantification-of-utility-of-atmospheric-network-technologies/). The WPS aims to perform a transparent long-term evaluation of a subset of commercially available LCS technologies for outdoor air pollution monitoring in background UK urban environments and is focused on key pollutants of interest: nitrogen dioxide (NO2), ozone (O3), and particulate matter (PM). Nine commercial sensor device companies elected to participate, all of them contributing duplicate or triplicate units with the ability to run continuously and report high time resolution data in near real-time via API. All the devices were deployed in Manchester in June 2021 and were installed as per manufacturer recommendations. The chosen site provides extensive reference measurements in a chemical range representative of UK urban environments. To ensure data integrity, given that all the assessed brands provide and store the data through their own data servers, a daily scrape was performed to transfer the measurement data to a secure server at the University of York. To ensure impartiality and consistency, device calibrations were performed by the manufacturers without any intervention from our team, and all reference data was embargoed until it was released to all manufacturers simultaneously. All data from this study will be made publicly available, along with the wider QUANT data, before February 2023.

If you have any questions please contact Sebastian Diez (`sebastian.diez@york.ac.uk`) or Pete Edwards (`pete.edwards@york.ac.uk`).

## Study period

```{r}
if (CALS_2_START == as_date("2022-03-01")) {
    msg <- "Our records indicate that you did not apply any calibration changes so the evaluation period comprises 1st March 2022 to 14th June 2022."
} else {
    msg <- sprintf("Our records indicate that you made changes to the calibration processes so the evaluation period comprises from this date %s to 14th June 2022", format(as_date(CALS_2_START), format='%d %b %Y'))
}
```

This report is the second and final of the WPS supplier evaluation reports and covers the agreed extension period between 1st March and 14th June 2022. The first report spanned July 2021 to January 2022 following the first calibration period. At the end of January 2022, reference data for PM2.5, NO2 and O3 from December 2021 were shared with all study participants allowing for further calibration adjustments to be made. `r msg` These dates are based on communications with suppliers, so if you feel the dates are not correct, please contact the QUANT team.

## Manchester Supersite

The Manchester Air Quality Supersite (MAQS) (located at 53$\text{\textdegree}$ 26' 39.2"N, 2$\text{\textdegree}$ 12' 51.9"W) was chosen because it is one of the largest air quality research facilities in the UK, and also because it is located in the south of the city of Manchester (one of the biggest metropolitan areas in the UK, with approximately 3.3 million inhabitants) in an urban background environment (average winter-time temperature of around 4-5 $\text{\textdegree}$C and \~87% RH; average summer-time temperature of around 16-17 $\text{\textdegree}$C and \~88% RH). The research-grade instrumentation at the MAQS used for this analysis are:

-   NO2: a Cavity Attenuated Phase Shift Spectroscopy (CAPS) NO2 analyzer (Teledyne, T500. Limit of detection \<40 ppt, root mean square "zero" noise \<20 ppt)
-   O3: a UV photometric O3 analyzer (Thermo Scientific, 49i. Limit of detection \<1.0 ppb, root mean square "zero" noise \<0.25 ppb)
-   PM: an optical aerosol spectrometer (Palas, FIDAS200. Mass range 0-10000 μ$\text{g/m}^3$, particle size range 0.18-18μm)

There was a fault with the FIDAS in March 2022 resulting in PM2.5 measurements not being available until the 29th March 2022. Furthermore, NO2 and O3 measurements from May 2022 onwards have not undergone ratification, otherwise all other measurements have been ratified.

## Evaluation methodology

No post-processing (for example no outlier removal or corrections) has been applied to the measurement data beyond averaging at an hourly rate to facilitate comparison with the co-located reference data. The species under evaluation are whichever are available out of NO2, O3, and PM2.5 and will be assessed for their accuracy by comparison to reference data by means of 4 methods:

-   A time-series plot allowing for visual inspection of any overall longitudinal trends
-   A scatter plot assessing the linearity of the sensor system, along with the $R^2$ and Root Mean Square Error (RMSE) summary metrics
-   A Bland-Altman plot to ascertain the nature of the errors and whether they follow a homoscedastic relationship with respect to the quantity being measured
-   A plot of the Relative Expanded Uncertainty (REU) along with the relevant Data Quality Objectives (DQO) and Limit Values (LV)

It is important to note that the results displayed in this summary only reflect the performance at the study location and in the study time window, and may be affected by factors external to the LCS system, for example the distance the system is installed from the inlet. Furthermore, the reference data has not been fully ratified during this time-frame. **As such, these results cannot be extrapolated to either future time-periods, alternative field locations, or both.**

## Relative Expanded Uncertainty Parameters

The Relative Expanded Uncertainty (REU) that forms one of the assessment pillars in this report is particularly appealing for its ability to explicitly account for uncertainty in the comparison reference data, rather than treating it as entirely error-free. An additional benefit of the REU is the fact that it is being used by regulatory bodies to provide guidelines for permissible uncertainty (Data Quality Objectives (DQO)) at the designated limit values, which are displayed in Table \ref{tab:reuparams} along with the values used for the inherent uncertainty inherent in the reference instruments.

```{r reuparams, fig.pos="H"}
tab <- map_dfr(REU_PROPERTIES, identity, .id = "Species") %>%
    mutate(LV = round(LV),
           uncertainty=round(uncertainty, 2)) %>%
    select(Species, LV, DQO_pct, uncertainty) %>%
    kable("latex", booktabs=TRUE, align=c("l", "c", "c", "c"),
          col.names = c("Species", "Limit Value (ppb or ug/m3)", "DQO (%)", "Reference instrument uncertainty (ppb or ug/m3)"),
          escape = TRUE,
          caption="REU Parameters for O3, NO2, and PM2.5. Limit value and instrument uncertainity units are ppb for NO2 and O3 and ug/m3 for PM2.5") %>%
    kable_styling(full_width=FALSE, latex_options = "HOLD_position")
tab
```

\newpage

# Field Results

## Data availability

Table \ref{tab:avail} summarises the data availability from the deployed low cost sensors throughout the duration of this project.

```{r avail, fig.pos="H"}
tab_df <- comb %>%
    rename(Device=device) %>%
    group_by(Device, species) %>%
    summarise(n_avail = sum(!is.na(lcs), na.rm=T),
              lab = sprintf("%d (%.1f%%)", n_avail, n_avail / length(all_hours) * 100)) %>%
    filter(n_avail > 0) %>%
    select(-n_avail) %>%
    ungroup() %>%
    mutate(lab = ifelse(is.na(lab), "-", lab),
           species=factor(species, levels=c("O3", "NO2", "PM2.5"))) %>%
    pivot_wider(names_from=species, values_from=lab)
tab_df %>%
    kable("latex", align=c("l", rep('c', ncol(tab_df)-1)), booktabs=TRUE,
          caption=sprintf("Data availabilty from the low-cost devices. The columns show the number of hours with at least one valid measurement out of a maximum possible %d", length(all_hours))) %>%
    add_header_above(c(" "=1, "Number of hours of data available"=ncol(tab_df)-1)) %>%
    kable_styling(full_width=F, latex_options = "HOLD_position")
```

```{r}
plot_species <- function(in_species, units) {
    df <- comb %>%
            filter(species == in_species) |>
            group_by(device) %>%
            filter(sum(!is.na(lcs)) > 0) %>%  # Drop devies that have no valid measurements for this species
            ungroup() |>
            mutate(device = as.factor(device))
    
    p_ts <- df %>%
                pivot_longer(c(lcs, ref), names_to="type") %>%
                mutate(type = factor(type, levels=c("lcs", "ref"),
                                     labels=c("LCS", "Reference"))) %>%
                ggplot() +
                    geom_line(aes(x=timestamp, y=value, colour=type), na.rm=T, alpha=0.3) +
                    facet_wrap(~device, ncol=1, drop = FALSE) +
                    scale_colour_manual("", values=c("Black", "Red")) +
                    scale_x_datetime(date_labels="%b") +
                    theme_bw() +
                    guides(colour="none") +
                    theme(
                        panel.grid.minor = element_blank()
                    ) +
                    labs(x="", y=sprintf("[%s] (%s)", in_species, units))
    
    stats <- df %>%
        filter(!is.na(lcs), !is.na(ref)) |>
        group_by(device) %>%
        nest() %>%
        mutate(models = lapply(data, function(df) lm(lcs ~ ref, data=df)),
               eq = lapply(models, function(mod) sprintf("*y* = %.2f*x* %s %.1f", coef(mod)[2], ifelse(sign(coef(mod)[1]) == 1, "+", ""), coef(mod)[1])),
               r2 = lapply(models, function(mod) summary(mod)$r.squared),
               rmse = lapply(data, function(df) sqrt(mean((df$ref - df$lcs)**2, na.rm=T)))) %>%
        unnest(c(r2, rmse, eq)) %>%
        ungroup() %>%
        select(device, r2, rmse, eq) %>%
        mutate(r2 = sprintf("*R*<sup>2</sup> = %.2f", r2),
               rmse = sprintf("RMSE = %.2f", rmse),
               lab2 = sprintf("%s<br>%s<br>%s", eq, r2, rmse))
    
    p_scatter <- df %>%
                ggplot(aes(x=ref, y=lcs)) +
                    geom_pointdensity(na.rm=T) +
                    geom_abline(slope=1, intercept=0, colour="steelblue", linewidth=0.7) +
                    geom_smooth(method="lm", colour="red", linewidth=0.7, na.rm=T) +
                    facet_wrap(~device, ncol=1, drop=FALSE) +
                    scale_x_continuous(expand=expansion(c(0, 0.5))) +
                    scale_y_continuous(expand=expansion(c(0, 0.5))) +
                    geom_richtext(aes(x=-Inf, y=Inf, label=lab2), data=stats, fill=NA, label.color=NA, vjust=1.1, hjust=0, size=4) +
                    theme_bw() +
                    scale_colour_viridis_c() +
                    guides(colour="none") +
                    theme(
                        panel.grid.minor = element_blank(),
                        axis.title.x = element_text(size=10)
                    ) +
                    labs(x=sprintf("Reference [%s] (%s)", in_species, units), 
                         y=sprintf("LCS [%s] (%s)", in_species, units))
    
    df_ab <- df %>%
                mutate(error = ref - lcs, avg = (ref + lcs) / 2) %>%
                group_by(device) %>%
                summarise(mean = mean(error, na.rm=T),
                          sd = sd(error, na.rm=T)) %>%
                mutate(lower = mean - 1.96 * sd,
                       upper = mean + 1.96 * sd)
    
    p_ab <- df %>%
                mutate(error = ref - lcs, avg = (ref + lcs) / 2) %>%
                ggplot(aes(x=avg, y=error)) +
                    geom_pointdensity(na.rm=T) +
                    geom_hline(aes(yintercept=lower), data=df_ab, linetype="dashed", colour="red") +
                    geom_hline(aes(yintercept=mean), data=df_ab, linetype="dashed", colour="steelblue") +
                    geom_hline(aes(yintercept=upper), data=df_ab, linetype="dashed", colour="red") +
                    facet_wrap(~device, ncol=1, drop=FALSE) +
                    scale_colour_viridis_c() +
                    guides(colour="none") +
                    theme_bw() +
                    theme(
                        panel.grid.minor = element_blank(),
                        axis.title.x = element_text(size=10)
                    ) +
                    labs(x="Average Reference and LCS", y=sprintf("Error (%s)", units))
    
    reu_res <- reu(df$ref, df$lcs, u_ref=REU_PROPERTIES[[in_species]][["uncertainty"]])
    p_reu <- df %>%
        mutate(reu = ifelse(is.na(lcs) | is.na(ref), NA, reu_res)) |>
        filter(reu> 0, reu< 200) %>%
        ggplot(aes(x=ref, y=reu)) +
            geom_pointdensity() +
            #stat_smooth(se = FALSE) +
            geom_vline(xintercept = REU_PROPERTIES[[in_species]][["LV"]], linetype="dashed", colour="red") +
            geom_hline(yintercept = REU_PROPERTIES[[in_species]][["DQO_pct"]], linetype="dashed", colour="steelblue") +
            scale_colour_viridis_c() +
            guides(colour="none") +
            facet_wrap(~device, ncol=1, drop=FALSE) +
            ylim(0, 200) +
            labs(x=sprintf("Reference [%s] (%s)", in_species, units), 
                 y="REU (%)") +
            theme_bw() +
            theme(
                axis.title.x = element_text(size=10)
            )
    
    p <- plot_grid(p_ts, p_scatter, p_ab, p_reu, ncol=4)
    title <- ggdraw() + draw_label(sprintf("Comparison with reference - %s", in_species), fontface="bold")
    plot_grid(title, p, ncol=1, rel_heights=c(0.05, 1))
}
```

\newpage

## NO2

```{r, fig.height=8, fig.width=9, fig.cap="NO2 quantiative evaluation. Column 1: time-series plot of the LCS measurements (black) alongside reference (red). Column 2: Regression plot against reference data (blue and red lines are 1:1 and linear regression fit respectively). Column 3: Bland-Altman plot (blue line indicates mean error and the red lines represent 2 standard deviations). Column 4: Relative Expanded Uncertainty (REU) with the Limit Value and Data Quality Objectives shown by the dashed red and blue lines respectively. The blue solid line shows a non-linear line of best fit. The axes are restricted to REU values between 0 and 200% for clarity."}
if (comb %>% filter(species == "NO2", !is.na(lcs)) %>% nrow() > 1) {
    plot_species("NO2", "ppb")
} 
```

```{r, results='asis'}
if (comb %>% filter(species == "NO2", !is.na(lcs)) %>% nrow() == 0) {
    cat("No data available for this pollutant")
}
```

\newpage

## O3

```{r, fig.height=8, fig.width=9, fig.cap="O3 quantiative evaluation. Column 1: time-series plot of the LCS measurements (black) alongside reference (red). Column 2: Regression plot against reference data (blue and red lines are 1:1 and linear regression fit respectively). Column 3: Bland-Altman plot (blue line indicates mean error and the red lines represent 2 standard deviations). Column 4: Relative Expanded Uncertainty (REU) with the Limit Value and Data Quality Objectives shown by the dashed red and blue lines respectively. The blue solid line shows a non-linear line of best fit. The axes are restricted to REU values between 0 and 200% for clarity."}
if (comb %>% filter(species == "O3", !is.na(lcs)) %>% nrow() > 1) {
    plot_species("O3", "ppb")
}
```

```{r, results='asis'}
if (comb %>% filter(species == "O3", !is.na(lcs)) %>% nrow() == 0) {
    cat("No data available for this pollutant")
}
```

\newpage

## PM2.5

```{r, fig.height=8, fig.width=9, fig.cap="PM2.5 quantiative evaluation. Column 1: time-series plot of the LCS measurements (black) alongside reference (red). Column 2: Regression plot against reference data (blue and red lines are 1:1 and linear regression fit respectively). Column 3: Bland-Altman plot (blue line indicates mean error and the red lines represent 2 standard deviations). Column 4: Relative Expanded Uncertainty (REU) with the Limit Value and Data Quality Objectives shown by the dashed red and blue lines respectively. The blue solid line shows a non-linear line of best fit. The axes are restricted to REU values between 0 and 200% for clarity."}
if (comb %>% filter(species == "PM2.5", !is.na(lcs)) %>% nrow() > 1) {
    plot_species("PM2.5", "ug/m3")
}
```

```{r, results='asis'}
if (comb %>% filter(species == "PM2.5", !is.na(lcs)) %>% nrow() == 0) {
    cat("No data available for this pollutant")
}
```

\newpage

# Comparison with the first study period

This section places the above results into the context of the full Wider Participation study by showing the performance metrics of all deployed low-cost sensor systems from both the first evaluation period of July 2021 - January 2022 and this second period from 1st March 2022 until 14th June 2022. Figure \ref{fig:refdens} shows the difference in environmental conditions between these two time-ranges, with one covering the end of summer and Autumn, and the other Spring. Figure \ref{fig:bothstudycomp} shows the performance of all WPS participants according to their RMSE and R2 with the first evaluation period denoted by a circle and the second by a triangle. This comparison is provided solely as an illustrative figure and is **not** intended to be used as an exhaustive comparison, nor is it suitable for this purpose owing to the fact that this timeframe comprises non-overlapping recording periods and discrepencies regarding which calibrations have been applied.

```{r}
# Get device IDs of all WP devices
device_ids <- tbl(con, "lcsinstrument") %>%
                filter(company != 'RLS',
                       instrument != 'IMB1',  # Device failed March 2022
                       study == 'Wider Participation') |>
                select(device=instrument, company, webid=internalid) %>%
                collect()

evaluate_device <- function(device, start, end, reference) {
    lcs_df <- retrieve_lcs_data(device, start, end, params$species, avg=params$average)
    lcs_df %>%
         left_join(reference, by=c("timestamp", "measurand"), suffix=c("_lcs", "_ref")) %>%
         group_by(measurand) %>%
         summarise(rmse = sqrt(mean((measurement_lcs - measurement_ref)**2, na.rm=T)),
                   r2 = cor(measurement_ref, measurement_lcs, use="na.or.complete")**2) |>
        rename(species=measurand)
}

results <- device_ids %>%
    split(.$device) %>%
    map_dfr(function(x) evaluate_device(x$device, ALL_COMPARISON_2_START, STUDY_2_END, ref), .id="device")

# Add manufacturer names, flag if the current manufacturer
# And add the web-ready device id
results <- results %>%
    inner_join(device_ids, by="device") |>
    mutate(this_manufacturer = company == params$company_short) %>%
    select(-device) %>%
    rename(device=webid)

device_ord <- results %>%
    distinct(device, this_manufacturer) %>%
    arrange(desc(this_manufacturer)) %>%
    pull(device)

results$device <- factor(results$device, levels=device_ord)

# Remove species that aren't measured by this company
species_to_keep <- results %>%
    filter(this_manufacturer, !is.na(rmse)) %>%
    distinct(species) %>%
    pull(species)

results <- results %>%
            filter(species %in% species_to_keep)

# Get a handle to this company's device IDs (in webid format)
these_devices <- results %>%
                    filter(this_manufacturer) %>%
                    distinct(device) %>%
                    pull(device)
```

```{r}
ref_1 <- tbl(con, "ref") %>%
        filter(location == "Manchester",
               measurand %in% c(species_to_pull, "Temperature", "RelHumidity"),
               time >= EARLIEST_TIME_1, time <= STUDY_1_END) %>%
        select(timestamp=time, measurand, measurement) %>%
        mutate(timestamp = floor_date(timestamp, avg)) %>%
        group_by(timestamp, measurand) %>%
        summarise(measurement = mean(measurement, na.rm=T)) %>%
        ungroup() %>%
        collect()
```

```{r}
results_1 <- device_ids %>%
    split(.$device) %>%
    map_dfr(function(x) evaluate_device(x$device, ALL_COMPARISON_1_START, STUDY_1_END, ref_1), .id="device")

# Add manufacturer names, flag if the current manufacturer
# And add the web-ready device id
results_1 <- results_1 %>%
    inner_join(device_ids, by="device") |>
    mutate(this_manufacturer = company == params$company_short) %>%
    select(-device) %>%
    rename(device=webid)

device_ord_1 <- results_1 %>%
    distinct(device, this_manufacturer) %>%
    arrange(desc(this_manufacturer)) %>%
    pull(device)

results_1$device <- factor(results_1$device, levels=device_ord_1)

# Remove species that aren't measured by this company
species_to_keep_1 <- results_1 %>%
    filter(this_manufacturer, !is.na(rmse)) %>%
    distinct(species) %>%
    pull(species)

results_1 <- results_1 %>%
            filter(species %in% species_to_keep)

# Get a handle to this company's device IDs (in webid format)
these_devices_1 <- results_1 %>%
                    filter(this_manufacturer) %>%
                    distinct(device) %>%
                    pull(device)
```

```{r refdens, fig.height=4, fig.width=5, fig.cap="Reference data distributions between the two study periods"}
ref |>
    mutate(period = "2") |>
    rbind(ref_1 |> mutate(period = "1")) |>
    mutate(period = factor(period, levels=c(1, 2),
                           labels=c("July 2021 - Jan 2022",
                                    "March 2022 - June 2022"))) |>
    ggplot(aes(x=measurement, colour=period, fill=period)) +
        geom_density(alpha=0.3) +
        scale_fill_brewer("Time period", palette="Set1") +
        scale_colour_brewer("Time period", palette="Set1") +
        facet_wrap(~measurand, scales="free") +
        labs(x="Measurement (ppb/degree/%)",
             y="Density") +
        theme_bw() +
        theme(legend.position = "bottom")
```

```{r bothstudycomp, fig.width=8, fig.height=8, fig.cap="RMSE and R2 of all WPS devices between the first evaluation period (circle marker) and the second evaluation period (triangle marker)"}
all_res <- results |>
    mutate(study_period=2) |>
    rbind(results_1 |> mutate(study_period=1)) |>
    mutate(study_period = factor(study_period, levels=c(1, 2))) |>
    arrange(study_period)
all_res |>
    ggplot(aes(x=r2, y=rmse, group=device)) +
        geom_point(aes(fill=device, alpha=this_manufacturer, size=this_manufacturer, shape=study_period), na.rm=T) +
        geom_path(arrow=arrow(length=unit(0.2, "cm"), ends="last", type="open"),
                  linewidth=0.1,
                  alpha=0.4) +
        scale_shape_manual("", values=c(21, 24)) +
        scale_fill_manual("LCS",
                            values=c(brewer.pal(length(these_devices), "Set1"),
                                     rep("black", length(device_ord) - length(these_devices))),
                            limits=these_devices) +
        scale_alpha_manual(values=c(0.5, 1)) +
        facet_wrap(~species, scales="free_y",
                   ncol=1) +
        scale_size_manual(values=c(2.0, 3.0)) +
        guides(alpha="none", size="none", shape="none",
               fill = guide_legend(override.aes=list(shape = 21, size=3))) +
        theme_bw() +
        xlim(0.125, 1) +
        theme(legend.position = "bottom") +
        labs(y=TeX(r"(RMSE (ppb/$\mu gm^{-3}$) )"), x=TeX(r"($R^2$)"))
```

```{r}
dbDisconnect(con)
```
